\label{BIO151}  % Replace course code with ID - e.g. \label{CSC110}
\begin{enumerate}[1.]
\item Course number and name\\
  {\bfseries
    % Add course number and name
    % --------------------------
    BIO151, Molecular and Cell Biology and Genetics
  }
  
\item Credits and contact hours\\
  {\bfseries
    % Add Number of Credits and Contact Hours
    % ---------------------------------------
    4    
  }

\item Instructor's or course coordinator's name\\
  {\bfseries
    % Add Instructor name
    % -------------------
    Coordinator: Prof. Nancy Burns
  }

\item Text book, title, author, and year\\
  {\bfseries
    % Add Textbook info
    % --------------------------
    \begin{itemize}
    \item {\em A Student Handbook for Writing in Biology, 5th Edition}, Knisely, Karin, 2017.
    \item {\em Mastering Biology Online Study System, 12th Edition} (ISBN 9780135855836),
          Urry, L. A.,
          Cain, M. L.,
          Wasserman, S. A.,
          Minorsky, P. V.,
          Orr, R. B.,
          Campbell, N.A, 2020.
    \end{itemize}
  }
\begin{enumerate}[a.]
\item Other supplemental materials\\
  {\bfseries
    % List any other supplemental material
    % ------------------------------------
    None.    
  }
\end{enumerate}

\item Specific course information
\begin{enumerate}[a.]  
\item Catalog description of the content of the course\\
  {\bfseries
    % Add catalog description (taken from AY 2021-2022 catalog)
    % -----------------------
Students investigate key concepts in molecular and cell biology and genetics. Topics include evolution, the central dogma, regulation of gene expression, cell structure and physiology, cell communication, immunology, cancer and cell division.     
  }

\item prerequisites or co-requisites\\
  {\bfseries
    % List any pre/co requisites
    % --------------------------
    % None   % Uncomment if none
    Prerequisites: BIO150, BIO150L (Minimum Grade C-)\\    
    Corequisites: BIO151L
  }

\item indicate whether a required, elective, or selected elective\\ % (as per Table 5-1)
  {\bfseries
    % R, E, or S (uncomment)
    % --------------------------
    % Required
    % Elective
    Selected elective
  }

\end{enumerate}

\item Specific goals for the course
\begin{enumerate}
\item specific outcomes of instruction\\ % , for example, ``The student will be able to explain the significance of current research about a particular topic.'' \\
  {\bfseries
    % 
    % --------------------------
    Learning Objectives (the student will be able to):
    Outcomes are given as a list of topics (see below).
  }

\item explicitly indicate which of the student outcomes listed in Criterion 3 or any other outcomes are addressed by the course.\\
  {\bfseries
    None
    % C1,
    % C2,
    % C3,
    % C4,
    % C5,
    % C6
  }
\end{enumerate}

\item Brief list of topics to be covered\\
  {\bfseries
    Lecture Topics
    \begin{itemize}
    \item Gene Expression. 
How do the molecular structures of DNA, RNA, and protein enable expression of the same information in the three different kinds of molecules? What is the genetic code and how was it elucidated? What are the roles of ribosomes, tRNA, rRNA, and mRNA in protein synthesis?  What major kinds of regulation of gene expression are exhibited in prokaryotes? How is this system more complicated in the multicellular eukaryotic descendants of prokaryotes? 
    \item Cell Communication.
How do cells receive and interpret information from their surrounding environment?  How do cells communicate with one another? What are the major signaling pathways in eukaryotic cells and how do they influence cell behavior?  What are the apoptotic pathways and what signals trigger them? What is the cell cycle?  How do cyclin and cyclin-dependent kinases influence cell cycles? How does loss of cell cycle control lead to cancer? 

    \item Genetics.
What are the fundamental processes of meiosis? How are the traits of parents transmitted to their offspring? How is genetic variation produced and the evolutionary importance of this variation? What two laws of inheritance did Gregor Mendel discover using a scientific approach? What is the importance of Morgan’s discovery and how does it apply to patterns of inheritance? How do alterations of chromosome number or structure result in a genetic disorder? What are non-Mendelian patterns of inheritance?

     \item Evolution.
What is the central dogma of biology and how does it relate to the biological capabilities of the hereditary molecule, to the very existence and nature of evolution? What are viruses and how do they replicate? What are the key concepts of Darwin’s Theory of evolution? What is the biological species concept? How does natural selection influence adaptive evolution? What roles do genetic drift and gene flow have in natural selection? How has life evolved?
    \end{itemize}
  }
\end{enumerate}

\noindent Prepared by: Christian Duncan\\
\noindent Creation date: 06/26/2021\\
\noindent Revised:\\
