\label{CSC111}  % Replace course code with ID - e.g. \label{CSC110}
\begin{enumerate}[1.]
\item Course number and name\\
  {\bfseries
    % Add course number and name
    % --------------------------
    CSC 111, Data Structures and Abstraction
  }
  
\item Credits and contact hours\\
  {\bfseries
    % Add Number of Credits and Contact Hours
    % ---------------------------------------
    3  % Default, change if needed
  }

\item Instructor's or course coordinator's name\\
  {\bfseries
    % Add Instructor name
    % -------------------
    Stefan Christov
  }

\item Text book, title, author, and year\\
  {\bfseries
    % Add Textbook info
    % --------------------------
    {\em Data Abstraction and Problem Solving with Java: Walls and Mirrors (3rd Edition)} by Janet Prichard and Frank Carrano, 2010
  }
\begin{enumerate}[a.]
\item Other supplemental materials\\
  {\bfseries
    % List any other supplemental material
    % ------------------------------------
    
  }
\end{enumerate}

\item Specific course information
\begin{enumerate}[a.]  
\item Catalog description of the content of the course\\
  {\bfseries
    % Add catalog description
    % -----------------------
    This course is a continuation of CSC110. Topics include advanced data structures
(linked lists, stacks, queues, and trees), recursion, abstract data types,
sorting and search algorithms, and object-oriented programming.
  }

\item prerequisites or co-requisites\\
  {\bfseries
    % List any pre/co requisites
    % --------------------------
    % None   % Uncomment if none
    Prerequisites: CSC110, CSC110L (Minimum Grade C-) \\  % Just some defaults
    Corequisites: CSC111L
  }

\item indicate whether a required, elective, or selected elective\\ % (as per Table 5-1)
  {\bfseries
    % R, E, or S (uncomment)
    % --------------------------
    Required
    % Elective
    % Selected elective
  }

\end{enumerate}

\item Specific goals for the course
\begin{enumerate}
\item specific outcomes of instruction\\ % , for example, ``The student will be able to explain the significance of current research about a particular topic.'' \\
  {\bfseries
    % 
    % --------------------------
    Course Learning Objectives (the student will be able to):
    \begin{itemize}
     	 \item Design, write, document, and test sophisticated programs using an object-oriented language.
   	 \item Identify situations where recursion is an appropriate problem solving strategy.
   	 \item Compare array and linked data structures and implement problem solutions using each.
   	 \item Describe the characteristics of stack and queue data structures and implement problem solutions using each.
   	 \item Describe characteristics of tree data structures and implement problem solutions using them.
   	 \item Explain search and sorting methods and implement programs using each.
   	 \item Describe factors that determine algorithm efficiency and measure the efficiency of searching and sorting algorithms.
    \end{itemize}
  }

\item explicitly indicate which of the student outcomes listed in Criterion 3 or any other outcomes are addressed by the course.\\
  {\bfseries
    C1 (CLOs 1-7), 
    C2 (CLOs 1,7),
    C3 (CLO 1), 
    C6 (CLOs 1-7)
    % C1 (CLO ...),
    % C2 (CLO ...),
    % C3 (CLO ...),
    % C4 (CLO ...),
    % C5 (CLO ...),
    % C6 (CLO ...)
  }
\end{enumerate}

\item Brief list of topics to be covered\\
  {\bfseries
    Lecture Topics
    \begin{itemize}
      \item Course intro, Java: syntax, branching, loops, program structure
      \item Object-oriented programming: classes and objects
      \item Java: standard I/O,  file I/O, exceptions
      \item Recursion
      \item Algorithm efficiency, linear search, binary search
      \item Sorting algorithms: selection sort, bubble sort, insertion sort, merge sort, quick sort
      \item ADTs; List ADT, List implementations: array-based and linked list
      \item Stacks, Postfix notation
      \item Queues
      \item Trees
      \item Hashing
    \end{itemize}
  }

\end{enumerate}

\noindent Prepared by: Stefan Christov\\
\noindent Creation date: 06/29/2021\\
\noindent Revised:\\
