\label{CSC375-Cloud}  % Replace course code with ID - e.g. \label{CSC110}
\begin{enumerate}[1.]
\item Course number and name\\
  {\bfseries
    % Add course number and name
    % --------------------------
    CSC375, Cloud Computing
  }

\item Credits and contact hours\\
  {\bfseries
    % Add Number of Credits and Contact Hours
    % ---------------------------------------
    3
  }

\item Instructor's or course coordinator's name\\
  {\bfseries
    % Add Instructor name
    % -------------------
    Solomon Abiola (Prof. Jonathan Blake)
  }

\item Text book, title, author, and year\\
  {\bfseries
    % Add Textbook info
    % --------------------------
    N/A (Online resources will be used)
  }
\begin{enumerate}[a.]
\item Other supplemental materials\\
  {\bfseries
    % List any other supplemental material
    % ------------------------------------
    Supplemental material provided on Blackboard
  }
\end{enumerate}

\item Specific course information
\begin{enumerate}[a.]
\item Catalog description of the content of the course\\
  {\bfseries
    % Add catalog description
    % -----------------------
General Catalog Description: This course explores advanced computer science topics not available in other courses, as well as new topics as they emerge in this rapidly evolving discipline. Topics may be interdisciplinary.

Specific Course Description: This introductory 3 credit course provides a hands-on approach to cloud computing. Through this course students will be exposed to a wide variety of cloud computing providers, concepts, and projects. This course will specifically cover in detail Google’s Cloud Platform and Amazon’s Web Services. At the completion of this course students will be familiar with key cloud concepts. Will develop their own cloud project and be prepared to sit for one of the cloud certification exams on either cloud platform.
  }

\item prerequisites or co-requisites\\
  {\bfseries
    % List any pre/co requisites
    % --------------------------
    % None   % Uncomment if none
    Prerequisites: CSC215 and SER225 (Minimum Grade C-)
    % Corequisites:
  }

\item indicate whether a required, elective, or selected elective\\ % (as per Table 5-1)
  {\bfseries
    % R, E, or S (uncomment)
    % --------------------------
    % Required
    % Elective
    Selected elective
  }

\end{enumerate}

\item Specific goals for the course
\begin{enumerate}
\item specific outcomes of instruction\\ % , for example, ``The student will be able to explain the significance of current research about a particular topic.'' \\
  {\bfseries
    %
    % --------------------------
    None listed in syllabus
  }

\item explicitly indicate which of the student outcomes listed in Criterion 3 or any other outcomes are addressed by the course.\\
  {\bfseries
    None
    % C1,
    % C2,
    % C3,
    % C4,
    % C5,
    % C6
  }
\end{enumerate}

\item Brief list of topics to be covered\\
  {\bfseries
    Lecture Topics
    \begin{itemize}
      \item Overview of Cloud Computing
      \item Cloud Service Models – IaaS, PaaS, SaaS
      \item Cloud Computing Components – Virtual Machines, Servers,
      \item Cloud Computing Services
      \item Infrastructure – Availability Zones, Regions, Edge Locations
      \item Hands On – Exploring the various main services in GCP/AWS
      \item Pricing and Billing in GCP/AWS
      \item Security in the Cloud
      \item Databases and Networking in the Cloud
      \item Big Data and Machine Learning in the Cloud
    \end{itemize}
  }

\end{enumerate}

\noindent Prepared by: Christian Duncan\\
\noindent Creation date: 06/28/2021\\
\noindent Revised: Jonathan Blake (06/28/2021)\\
