\label{CSC375-DevOps}  % Replace course code with ID - e.g. \label{CSC110}
\begin{enumerate}[1.]
\item Course number and name\\
  {\bfseries
    % Add course number and name
    % --------------------------
    CSC375, Introduction to DevOps
  }

\item Credits and contact hours\\
  {\bfseries
    % Add Number of Credits and Contact Hours
    % ---------------------------------------
    3
  }

\item Instructor's or course coordinator's name\\
  {\bfseries
    % Add Instructor name
    % -------------------
    Prof. Justin Kohlhepp
  }

\item Text book, title, author, and year\\
  {\bfseries
    % Add Textbook info
    % --------------------------
    The DevOps Handbook by Gene Kim, Jez Humble, Patrick Debois, and John Willis. ISBN 1942788002 / 978-1942788003.
  }
\begin{enumerate}[a.]
\item Other supplemental materials\\
  {\bfseries
    % List any other supplemental material
    % ------------------------------------
    Supplemental Reading:

    The Phoenix Project by Gene Kim, Jez Humble, Patrick Debois, and John Willis
  }
\end{enumerate}

\item Specific course information
\begin{enumerate}[a.]
\item Catalog description of the content of the course\\
  {\bfseries
    % Add catalog description
    % -----------------------
General Catalog Description: This course explores advanced computer science topics not available in other courses, as well as new topics as they emerge in this rapidly evolving discipline. Topics may be interdisciplinary.

Specific Course Description: This course acquaints students with various aspects of DevOps, an emerging concept in software engineering covering a variety of techniques and technologies. Students learn about the fundamental principles underlying the DevOps movement, as well as specific techniques and the technologies used to employ those techniques.  This includes continuous integration, continuous deployment, automated builds and testing, continuous monitoring, DevSecOps, and more.  Students will also be exposed to related concepts in software delivery, such as Agile software development.
  }

\item prerequisites or co-requisites\\
  {\bfseries
    % List any pre/co requisites
    % --------------------------
    % None   % Uncomment if none
    Prerequisites: CSC215 and SER225 (Minimum Grade C-)
    % Corequisites:
  }

\item indicate whether a required, elective, or selected elective\\ % (as per Table 5-1)
  {\bfseries
    % R, E, or S (uncomment)
    % --------------------------
    % Required
    % Elective
    Selected elective
  }

\end{enumerate}

\item Specific goals for the course
\begin{enumerate}
\item specific outcomes of instruction\\ % , for example, ``The student will be able to explain the significance of current research about a particular topic.'' \\
  {\bfseries
    %
    % --------------------------
    Course Learning Outcomes:

    By the completion of this course, students will be able to:
\begin{enumerate}
\item Demonstrate an overall understanding of DevOps concepts and how they apply in real-world software engineering scenarios
\item Design automated build, test, and deployment scripts for use in software systems
\item Understand how to analyze processes the contribute to the software delivery value stream
\item Demonstrate techniques that allow for collaborative evolution of complex software projects
\end{enumerate}
  }

\item explicitly indicate which of the student outcomes listed in Criterion 3 or any other outcomes are addressed by the course.\\
  {\bfseries
    None
    % C1,
    % C2,
    % C3,
    % C4,
    % C5,
    % C6
  }
\end{enumerate}

\item Brief list of topics to be covered\\
  {\bfseries
    \begin{itemize}
      \item What is DevOps
      \item Continuous Integration
      \item Continuous Testing
      \item Source Control Techniques
      \item Continuous Release
      \item Continuous Monitoring
      \item Continuous Exploration
      \item Continuous Quality
      \item Continuous Learning
      \item Continuous Collaboration / ChatOps
      \item Continuous Security
      \item Continuous Change Management / Auditability
      \item DevOps Organizations
    \end{itemize}
  }

\end{enumerate}

\noindent Prepared by: Christian Duncan\\
\noindent Creation date: 06/28/2021\\
\noindent Revised: Jonathan Blake (06/28/2021)\\
