\label{MA285}  % Replace course code with ID - e.g. \label{CSC110}
\begin{enumerate}[1.]
\item Course number and name\\
  {\bfseries
    % Add course number and name
    % --------------------------
    MA285, Applied Statistics    
  }
  
\item Credits and contact hours\\
  {\bfseries
    % Add Number of Credits and Contact Hours
    % ---------------------------------------
    3  % Default, change if needed
  }

\item Instructor's or course coordinator's name\\
  {\bfseries
    % Add Instructor name
    % -------------------
    K. James Soda    
  }

\item Text book, title, author, and year\\
  {\bfseries
    % Add Textbook info
    % --------------------------
    Probability and Statistics for Engineering and the Sciences, Jay L. Devore, 2015
  }
\begin{enumerate}[a.]
\item Other supplemental materials\\
  {\bfseries
    % List any other supplemental material
    % ------------------------------------
    Access to WebAssign, laptop with R (programming language) installed
  }
\end{enumerate}

\item Specific course information
\begin{enumerate}[a.]  
\item Catalog description of the content of the course\\
  {\bfseries
    % Add catalog description
    % -----------------------
This introductory statistics course is intended primarily for students majoring in engineering, mathematics or the sciences. Emphasis is on using statistics to answer questions in the physical and social sciences. Topics include descriptive statistics, probability, point and interval estimation, hypothesis testing, correlation and regression, analysis of variance, chi-square tests and nonparametric methods. Students are required to analyze real data sets using Excel, SAS, SPSS or similar computer programs. Students are not allowed to receive credit for more than one of the following courses: MA 206, MA 275 and MA 285.    
  }

\item prerequisites or co-requisites\\
  {\bfseries
    % List any pre/co requisites
    % --------------------------
    % None   % Uncomment if none
    Prerequisites: MA141, MA151 (Minimum Grade C-) \\  % Just some defaults
    % Corequisites: 
  }

\item indicate whether a required, elective, or selected elective\\ % (as per Table 5-1)
  {\bfseries
    % R, E, or S (uncomment)
    % --------------------------
    % Required
    % Elective
    Selected elective
  }

\end{enumerate}

\item Specific goals for the course
\begin{enumerate}
\item specific outcomes of instruction\\ % , for example, ``The student will be able to explain the significance of current research about a particular topic.'' \\
  {\bfseries
    % 
    % --------------------------
    Course Learning Objectives (the student will be able to):
    \begin{enumerate}[1.]
\item Students will describe real-world data using descriptive statistics and
visualizations and will identify patterns in the data using these tools.
\item Students will associate real-world systems with probability distributions
and use these distributions to answer scientific questions.
\item Students will use tools from probability theory and statistics to describe
systems whose attributes vary, estimate common values for these
attributes, and provide uncertainty quantification for these estimates.
\item Students will use statistical inference to assess the veracity of hypotheses
in the natural, social, and applied sciences.
\item Students will use the relationship between two or more random variables
to infer functional relationships in empirical systems and predict unknown
states of these systems.
\item Students will evaluate the effectiveness of a statistical analysis to discern
whether the analysis’s conclusions are valid.
\item Students will implement common statistical techniques using R.
    \end{enumerate}
  }

\item explicitly indicate which of the student outcomes listed in Criterion 3 or any other outcomes are addressed by the course.\\
  {\bfseries
    None
    % C1 (CLO ...),
    % C2 (CLO ...),
    % C3 (CLO ...),
    % C4 (CLO ...),
    % C5 (CLO ...),
    % C6 (CLO ...)
  }
\end{enumerate}

\item Brief list of topics to be covered\\
  {\bfseries
    Lecture Topics
    \begin{itemize}
\item Introduction to Statistics, Data, and R
\item Data Visualization
\item Probability Spaces and Functions
\item Bernoulli Trials and Associated Distributions
\item Continuous Random Variables
\item Normal Distribution
\item Poisson Processes
\item Point Estimators
\item Confidence Intervals
\item Principles of Hypothesis Testing
\item One-Factor ANOVA
\item Joint Probability
\item Contingency Tables
\item Covariance and correlation
\item Regressions (Linear, Mutliple, Curvilinear)
\item Non-parametric Tests
\item Likelihood
\end{itemize}
  }

\end{enumerate}

\noindent Prepared by: Christian Duncan\\
\noindent Creation date: 06/26/2021\\
\noindent Revised:\\
