\label{SER225}  % Replace course code with ID - e.g. \label{CSC110}
\begin{enumerate}[1.]
\item Course number and name\\
  {\bfseries
    % Add course number and name
    % --------------------------
    SER 225, Introduction to Software Development
  }

\item Credits and contact hours\\
  {\bfseries
    % Add Number of Credits and Contact Hours
    % ---------------------------------------
    3  % Default, change if needed
  }

\item Instructor's or course coordinator's name\\
  {\bfseries
    % Add Instructor name
    % -------------------
    Mark Hoffman
  }

\item Text book, title, author, and year\\
  {\bfseries
    % Add Textbook info
    % --------------------------
    The Pragmatic Programmer, Andrew Hunt and David Thomas, 2000.\\
    The Mythical Man-Month, F.P. Brooks, 1995.\\
    The Case of the Killer Robot, Richard G. Epstein, 1997.
  }
\begin{enumerate}[a.]
\item Other supplemental materials\\
  {\bfseries
    % List any other supplemental material
    % ------------------------------------
    A code base for a software system that students maintain as part of a semester-long project
  }
\end{enumerate}

\item Specific course information
\begin{enumerate}[a.]
\item Catalog description of the content of the course\\
  {\bfseries
    % Add catalog description
    % -----------------------
    This course presents introductory software engineering concepts including group development, large-scale project work, and theoretical aspects of object-oriented programming. The course expands on material from previous courses. Professional behavior and ethics represent an important component of this course.
  }

\item prerequisites or co-requisites\\
  {\bfseries
    % List any pre/co requisites
    % --------------------------
    % None   % Uncomment if none
    Prerequisites: CSC 111, CSC111L (Minimum Grade C-) \\  % Just some defaults
    % Corequisites:
  }

\item indicate whether a required, elective, or selected elective\\ % (as per Table 5-1)
  {\bfseries
    % R, E, or S (uncomment)
    % --------------------------
    Required
    % Elective
    % Selected elective
  }

\end{enumerate}

\item Specific goals for the course
\begin{enumerate}
\item specific outcomes of instruction\\ % , for example, ``The student will be able to explain the significance of current research about a particular topic.'' \\
  {\bfseries
    %
    % --------------------------
    Course Learning Objectives (the student will be able to):
    \begin{itemize}
      \item Evaluate and maintain an existing software product.
      \item Develop clear, concise, and sufficiently formal life-cycle artifacts including requirements, design, implementation, and test documentation for software systems based on needs of users and stakeholders.
      \item Explain the value of construction technologies such as version control and design tools to assist the software development practice.
      \item Explain the purpose of testing and apply it to manage an existing software product.
      \item Work on a team and communicate, orally and in writing, a software design to various audiences.
      \item Explain the social and ethical implications of the software development process.
      \item Demonstrate the ability to think critically and be reflective learners.
    \end{itemize}
  }

\item explicitly indicate which of the student outcomes listed in Criterion 3 or any other outcomes are addressed by the course.\\
  {\bfseries
    C1 (CLOs 1-4),
    C2 (CLOs 1, 2),
    C3 (CLOs 2, 5),
    C4 (CLO 6),
    C5 (CLO 5),
    C6 (CLOs 1-4)
    % C1 (CLO ...),
    % C2 (CLO ...),
    % C3 (CLO ...),
    % C4 (CLO ...),
    % C5 (CLO ...),
    % C6 (CLO ...)
  }
\end{enumerate}

\item Brief list of topics to be covered\\
  {\bfseries
    Lecture Topics
    \begin{itemize}
      \item Customer requirements, user stories
      \item Test planning
      \item Bug identification and prioritization
      \item Version control
      \item Scrum process management
      \item Teamwork
      \item Presentation skills
      \item Ethics in software development
    \end{itemize}
  }

\end{enumerate}

\noindent Prepared by: Stefan Christov\\
\noindent Creation date: 06/29/2021\\
\noindent Revised:\\
